---
title: "Unifynd Interview Assessment (Data Analytics) R Notebook"
output:
  html_document:
    df_print: paged
---

# How to use this R Markdown notebook? 

* The main code file is an [R Markdown](http://rmarkdown.rstudio.com) Notebook, whose extension is **.Rmd**. You can preview this notebook using the **Preview** button, which will show you   rendered HTML copy of the contents of the editor. 

* The other option is to knit this notebook into a neat PDF, which you can do using the **Knit** button.
 
* Unlike **Knit**, **Preview** does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed. So, when you use **Preview**, please make sure that you have once run all the chunks of code in the editor. Once you run all chunks and then preview, the resulting html output will show all code and all output (plots, tables, etc).

* This notebook contains all code, output and answers, for all of the 7 Questions (and all its sub-parts).  

* I have also attached a complete pre-knitted PDF (with all code, output, answers) in my submission files (along side this .Rmd file).


```{r metadata}

# metadata---------------------------------------------------------------------
# author: Aarsh Batra
# Start Date: October 07, 2021
# R version: 4.1.1 (2021-08-10)
# nickname: Kick Things
# Platform: x86_64-w64-mingw32 
# arch: x86_64
# Running under: Windows 10 x64 (build 18363)
# R Studio version info: 2021.09.0+351 "Ghost Orchid"
# e-mail: aarshbatra.in@gmail.com

```

```{r loadLibraries}

# load libraries---------------------------------------------------------------

library(tidyverse)
library(knitr)
library(devtools)
library(stringr)
library(tidyr)
library(dplyr)
library(magrittr)
library(data.table)
library(lubridate)
library(roxygen2)
library(testthat)
library(ggplot2)
```
